Side-effects

### 2021-04-16 analysis/side-effects.Rmd
Data refresh

```{r}
SE <- mutate(
  SE,
  caller=str_replace(eval_call_srcref, "::(.*)::(.*)::.*", "\\1::\\2")
)
```

@@

```{r}
S_call <- sum(S$nb_ev_calls)
S_site <- count(S, eval_call_srcref)
S_package <- count(S, eval_source)
S_funs <- sum(PKG$funs_with_eval)

@@

SE_N <- sum(SE$N)
SE_calls <- count(SE, cid)
SE_sites <- count(SE, eval_call_srcref)
SE_funs <- count(SE, caller)
SE_pkgs <- count(SE, caller_package)
SE_missing_N <- sum(SE_missing_sites$N)

overview_table(
  r("All", SE_all_N),
  r("All calls", SE_all_calls),
  r("All sites", SE_all_sites),

@@

  r("User calls", SE_calls),
  r("User calls ratio", ratio(SE_calls, SE_all_calls)),

  r("User sites", SE_sites),
  r("User sites ratio", ratio(SE_sites, SE_all_sites)),

  r("User functions", count(SE, caller)),
  r("User packages", count(SE, caller_package)),
)
```

@@

```{r}
sum_sites_classes <- 
  sites_classes %>%
  mutate(
    classes=if_else(str_detect(classes, "[,;]"), "multiple", classes)
  ) %>%
  cs_count(classes) %>%
  mutate(
    p=fmt(p, suffix="\\%", digit=1),
    o=if_else(str_starts(classes, fixed("\\")), 0L, n)
  ) %>% 
  arrange(desc(o)) %>%
  select(-cp, -o)

sum_sites_classes %>%
  mutate(classes=if_else(classes=="multiple", "\\emph{multiple}", classes)) %>%
  xtable(
    align="llrr",
  ) %>%
  print(
    file=file.path(TAGS_DIR, "table-top-sites-classes-se.tex"),
    comment=FALSE, 
    include.colnames=FALSE,
    include.rownames=FALSE,
    only.contents=TRUE,
    sanitize.text.function=identity,
    timestamp=FALSE
  )
```

@@

```{r}
sum_funs_classes <-
funs_classes %>%
  filter(cov==1, classes != "") %>%
  mutate(
    classes=if_else(str_detect(classes, "[,;]"), "multiple", classes)
  ) %>%
  cs_count(classes) %>%
  mutate(
    p=fmt(p, suffix="\\%", digit=1),
    o=if_else(str_starts(classes, fixed("\\")), 0L, n)
  ) %>% 
  arrange(desc(o)) %>%
  select(-cp, -o)

sum_funs_classes %>%
  mutate(classes=if_else(classes=="multiple", "\\emph{multiple}", classes)) %>%
  xtable(
    align="llrr",
  ) %>% 
  print(
    file=file.path(TAGS_DIR, "table-top-sites-classes-funs.tex"),
    comment=FALSE, 
    include.colnames=FALSE,
    include.rownames=FALSE,
    only.contents=TRUE,
    sanitize.text.function=identity,
    timestamp=FALSE
  )
```

@@

left_join(
  select(event, event, n_event=n, p_event=p),
  select(event_calls, event, n_call=n, p_call=p),
  by="event"
) %>%
  left_join(
    select(event_site, event, n_site=n, p_site=p),
    by="event"
  ) %>% 
  mutate(event=case_when(
    event=="def" ~ "definition",
    event=="asn" ~ "update",
    event=="rvl" ~ "removal"
  )) %>%
  mutate_if(is.double, ~fmt(., suffix="%", digit=1)) %>%
  mutate_if(is.integer, ~fmt(.)) %>%
  xtable(
    align="llrrrrrr"
  ) %>%
  print(
    file=file.path(TAGS_DIR, "table-se-types.tex"),
    comment=FALSE, 
    include.colnames=FALSE,
    include.rownames=FALSE,
    only.contents=TRUE,
    timestamp=FALSE
  )
```

@@

>>>>

```{r}
SE <- mutate(
  SE,
  caller=str_replace(eval_call_srcref, "::(.*)::(.*)::.*", "\\1::\\2")
)

S <- mutate(
  S,
  caller=str_replace(eval_call_srcref, "::(.*)::(.*)::.*", "\\1::\\2"),
  caller_package=str_replace(eval_call_srcref, "::(.*)::.*::.*", "\\1")
)
```

@@

```{r}
S_calls <- sum(S$nb_ev_calls)
S_sites <- count(S, eval_call_srcref)
S_pkgs <- count(S, eval_source)
S_funs <- count(S, caller)

@@

SE_N <- sum(SE$N)
SE_calls <- count(SE, cid)
SE_sites <- count(SE, eval_call_srcref)
SE_funs <- count(SE, caller)
SE_pkgs <- count(SE, caller_package)
SE_missing_N <- sum(SE_missing_sites$N)
```

```{r}
overview_table(
  r("All", SE_all_N),
  r("All calls", SE_all_calls),
  r("All sites", SE_all_sites),

@@

  r("User calls", SE_calls),
  r("User calls ratio", ratio(SE_calls, SE_all_calls)),
  r("User calls to all ratio", ratio(SE_calls, S_calls)),

  r("User sites", SE_sites),
  r("User sites ratio", ratio(SE_sites, SE_all_sites)),
  r("User sites to all ratio", ratio(SE_sites, S_sites)),

  r("User functions", SE_funs),
  r("User functions to all ratio", ratio(SE_funs, S_funs)),
  r("User packages", SE_pkgs),
  r("User packages to all ratio", ratio(SE_pkgs, S_pkgs))
)
```

@@

```{r}
sum_sites_classes <- 
  sites_classes %>%
  mutate(
    classes=if_else(str_detect(classes, "[,;]"), "multiple", classes)
  ) %>%
  cs_count(classes) %>%
  mutate(
    p=fmt(p, suffix="\\%", digit=0),
    o=if_else(str_starts(classes, fixed("\\")), 0L, n)
  ) %>% 
  arrange(desc(o)) %>%
  select(-cp, -o)

# sum_sites_classes %>%
#   mutate(classes=if_else(classes=="multiple", "\\emph{multiple}", classes)) %>%
#   xtable(
#     align="llrr",
#   ) %>%
#   print(
#     file=file.path(TAGS_DIR, "table-top-sites-classes-se.tex"),
#     comment=FALSE, 
#     include.colnames=FALSE,
#     include.rownames=FALSE,
#     only.contents=TRUE,
#     sanitize.text.function=identity,
#     timestamp=FALSE
#  )
```

@@

```{r}
sum_funs_classes <-
  funs_classes %>%
    filter(cov==1, classes != "") %>%
    mutate(
      classes=if_else(str_detect(classes, "[,;]"), "multiple", classes)
    ) %>%
    cs_count(classes) %>%
    mutate(
      p=fmt(p, suffix="\\%", digit=0),
      o=if_else(str_starts(classes, fixed("\\")), 0L, n)
    ) %>% 
    arrange(desc(o)) %>%
    select(-cp, -o)

# sum_funs_classes %>%
#   mutate(classes=if_else(classes=="multiple", "\\emph{multiple}", classes)) %>%
#   xtable(
#     align="llrr",
#   ) %>% 
#   print(
#     file=file.path(TAGS_DIR, "table-top-sites-classes-funs.tex"),
#     comment=FALSE, 
#     include.colnames=FALSE,
#     include.rownames=FALSE,
#     only.contents=TRUE,
#     sanitize.text.function=identity,
#     timestamp=FALSE
#   )
```

@@

left_join(
  select(event, event, n_event=n, p_event=p),
  select(event_calls, event, n_call=n, p_call=p),
  by="event"
) %>%
  left_join(
    select(event_site, event, n_site=n, p_site=p),
    by="event"
  ) %>% 
  mutate(event=case_when(
    event=="def" ~ "definition",
    event=="asn" ~ "update",
    event=="rvl" ~ "removal"
  )) %>%
  mutate_if(is.double, ~fmt(., suffix="%", digit=0)) %>%
  mutate_if(is.integer, ~fmt(.)) %>%
  xtable(
    align="llrrrrrr"
  ) %>%
  print(
    file=file.path(TAGS_DIR, "table-se-types.tex"),
    comment=FALSE, 
    include.colnames=FALSE,
    include.rownames=FALSE,
    only.contents=TRUE,
    timestamp=FALSE
  )
```

@@

## Side effects with norm

```{r}
NE <- read_csv(
  PACKAGE_NORMALIZED_EXPRESSION_FILE,
  col_types = cols(
    minimized = col_character(),
    topcall = col_character(),
    is_model = col_double(),
    has_fundef = col_double(),
    has_calls = col_double(),
    has_assigns = col_double(),
    has_var = col_double(),
    has_bracket = col_double(),
    is_assign = col_double(),
    is_value = col_double(),
    is_ignore = col_double(),
    has_dollar = col_double(),
    has_user_call = col_double(),
    has_block = col_double(),
    has_meta_op = col_double(),
    normalized = col_character(),
    trimmed = col_character(),
    hash = col_character()
  )
) %>%
  select(
    minimized,
    topcall,
    normalized,
    expr_resolved_hash=hash
  )
```

```{r eval=F}
C <- read_fst(path(PACKAGE_DATA_DIR, "calls-sub.fst")) %>% as_tibble
CSE <- left_join(
  C,
  select(SE, cid, event, class, N),
  by="cid"
)
```
